\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-05-14 doc/sw-system.tex
checked through conclusions before writing method section

We draw the following conclusions:

@@

\item Crowd-sourced gravitational lens detection works, as shown on sims and
duds:

@@

\item Integrated humanpower = X, cf hours taken by small team of experts

@@

\item Completeness and purity were estimated as C\% and P\%, from sim and dud
recovery/miss rates. Which sims were missed? False negatives

>>>>

Summary of system.

Crowd-sourced gravitational lens detection works, in terms of the
classification of the training set as described here, in the following
specific ways:

@@

@@

\item Integrated humanpower = X (stage 1) and y (stage 2), cf hours taken by
small team of experts

@@

\item Retirement rate. False negatives: which sims were missed?

\item The optimal true positive rate (completeness) and false positive rate in
the training set were estimated to be TPR\% and FPR\% at Stage 1, assuming a
detection threshold of xxx.

\item In the ``refinement'' stage 2, X\% of the stage 1 candidates were
rejected (with P less than threshold), and the remainder assigned lens
``probabilities.'' Ranking
subjects by their Stage 2 lens probability gives an ROC curve for the system
with X properties. The optimal true positive rate (completeness) and false
positive rate in the training set were estimated as TPR\% and FPR\%;
